Hydrogen Epoch of Reionization Array (HERA)

### 2016-03-30 manuscript.tex
number of changes throughout, but mainly updated kperf figure

\begin{figure}[t]
	\centering
	\includegraphics[width=.56\textwidth]{plots/current_limits.pdf}
	\includegraphics[width=.43\textwidth]{plots/constraints_proposal.pdf}
	\vspace{-20pt}
	\caption{Left: The current best published $2\sigma$ upper limits on the 21cm power spectrum, $\Delta^2(k)$, (solid symbols represent analyses led by HERA collaborators) compared to 21cmFAST-generated models at $k=0.2$\,$h$\,Mpc$^{-1}$. 
Analysis is still underway on PAPER and MWA observations that approach their projected 
full sensitivities (see Fig.~\ref{fig:Sensitivities}); 
HERA can deliver sub-$\text{mK}^2$ sensitivities.
Right: The \citet{ali_et_al2015} limit at $z=8.4$ excludes the entire gray shaded area corresponding to a cold IGM \citep{pober_et_al2015}.  The color scale shows the power spectrum amplitude at $k = 0.25~h{\rm Mpc}^{-1}$ for a given spin temperature and neutral fraction.  Constraints are weaker if the (currently unknown) neutral fraction at $z=8.4$ is very high or low, as the 21\,cm signal is brightest during the middle of reionization.}
	\vspace{-10pt}
	\label{fig:limits}
	\label{fig:IGMtemperatureConstraints}
\end{figure}

@@

Though the desired measurement is over a volume, it is instructive to split it into two components,  $\kvec =  \kvpr + \kpar{\hat {\bf z}}$ where $\kvpr$ is determined by the antenna baseline and $\kpar$ by the frequency.  This is useful since it allows us to split out the chromatic response of the interferometer and isolate a phase space where foreground sources ({\em i.e.} everything {\em not} the EOR) contaminate the signal of interest from where they don't.  This contaminated phase space may be shown [REF] to be a wedge-shaped region in $\kpr$:$\kpar$ space:
\begin{equation}
|\kpar| \le \beta\frac{X\lambda}{Yc}\kpr + \frac{S}{Y}
\end{equation}
where $c$ is the speed of light and $S$ is a parameter accounting for offsets related to the combined spectral smoothness of the foregrounds and the antenna response (see Fig. \ref{fig:wedgeWithBG}).  
A key issue to measuring the EOR power spectrum is to understand and minimize such effects.  For an analytical derivation, see \cite{2012ApJ...756..165P,vedantham_et_al2012,liu_et_al2014b},  in simulation see \cite{datta_et_al2010,hazelton_et_al2013} and for observations
\cite{2013ApJ...768L..36P,2015arXiv150601026P,2014ApJ...788..106P,2015arXiv150206016A}.

@@

\begin{figure}[h!]
\centerline{
\includegraphics[width=\textwidth]{plots/kperf.png} 
}
\caption{\small k
\label{fig:kperf}}
\end{figure}

@@

From these measurements and models, the Phase 1 and 2 minimum spans of redshifts range from $z=$6 to 13, corresponding to a frequency range of 100 - 200 MHz.  Extending the science to include the Dark Ages remains a goal so that efforts are on-going to design a feed to increase the lower limit down to about 50 MHz without compromising the performance in the specification range.  The fall-back position for the low-frequencies is a serial deployment of a scaled version of the HERA feed or to potentially build additional elements specifically for the low-frequencies.  The 100 MHz bandwidth is also the minimum fully digitized and correlated bandwidth.

>>>>

\begin{figure}[t]
	\centering
	\includegraphics[width=.8\textwidth]{plots/current_limits.pdf}
	\caption{The current best published $2\sigma$ upper limits on the 21cm power spectrum, $\Delta^2(k)$, (solid symbols represent analyses led by HERA collaborators) compared to 21cmFAST-generated models at $k=0.2$\,$h$\,Mpc$^{-1}$. 
Analysis is still underway on PAPER and MWA observations that approach their projected 
full sensitivities (see Fig.~\ref{fig:Sensitivities}); 
HERA can deliver sub-$\text{mK}^2$ sensitivities.}
	\vspace{-10pt}
	\label{fig:limits}
	\label{fig:IGMtemperatureConstraints}
\end{figure}

@@

Though the desired measurement is over a volume, it is instructive to split it into two components,  $\kvec =  \kvpr + \kpar{\hat {\bf z}}$ where $\kvpr$ is determined by the antenna baseline and $\kpar$ by the frequency.  This is useful since it allows us to split out the chromatic response of the interferometer and isolate a phase space where foreground sources ({\em i.e.} everything {\em not} the EOR) contaminate the signal of interest from where they don't.  This contaminated phase space may be shown [REF] to be a wedge-shaped region in $\kpr$:$\kpar$ space:
\begin{equation}
|\kpar| \le \beta\frac{X\lambda}{Yc}\kpr + \frac{S}{Y}
\end{equation}
where $c$ is the speed of light and $S$ is a parameter accounting for offsets related to the combined spectral smoothness of the foregrounds and the antenna response (see Fig. \ref{fig:wedgeWithBG}).  
A key issue to measuring the EOR power spectrum is to understand and minimize such effects.  For an analytical derivation, see \cite{2012ApJ...756..165P,vedantham_et_al2012,liu_et_al2014b},  in simulation see \cite{datta_et_al2010,hazelton_et_al2013} and for observations
\cite{2013ApJ...768L..36P,2015arXiv150601026P,2014ApJ...788..106P,2015arXiv150206016A}.  Note that the unit of the spatial wavenumber $k$ is 1/length, in this case the relevant length scale is megaparsecs (Mpc; 1 Mpc = 3.086$\times10^{22}$ m).  In order to normalize for updated measurements of Hubble's constant, it is further normalized by $h$, where $H_o=100h$, such that they are expressed as $h$/Mpc.

@@

\begin{figure}[h!]
\centerline{
\includegraphics[width=.4\textwidth]{plots/kperf.png} 
}
\caption{\small k
\label{fig:kperf}}
\end{figure}

@@

From these measurements and models, HERA is required to cover a redshift range of $z=$6 to 13, corresponding to a frequency range of 101 - 203 MHz.  We adopt 100-200 MHz for full performance as the requirement.  Extending the science to include the Dark Ages remains a goal so that efforts are on-going to design a feed to increase the lower limit down to at least 70 MHz without compromising the performance in the above requirement range.  The fall-back position for the low-frequencies is a serial deployment of a scaled version of the HERA feed or to potentially build additional elements specifically for the low-frequencies.  The 100 MHz bandwidth is also the minimum fully digitized and correlated bandwidth.
